A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Code formatting

```{r Figure2, echo=FALSE, fig.cap="Season plot"}
PM_Mdat %>%
  distinct(trial_ref, planting_date, harvest_date,first_sign_disease) %>%
  mutate(planting_date = ymd(planting_date))%>%
  mutate(harvest_date = ymd(harvest_date))%>%
  mutate(first_sign_disease = ymd(first_sign_disease))%>%
  mutate(cropping_season = case_when( # add categorical value for estimated season period
    is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
    TRUE ~ "Actual"))%>%
  mutate(plant_day = case_when( #for crops planted in late December minus 365 days from yday function
    yday(planting_date) < 200 ~ yday(planting_date),
    yday(planting_date) > 200 ~ yday(planting_date) - 365,
  )) %>%
  mutate(season_length = case_when(  # when either planting date or harvest date are missing use the overall mean season length as an estimate
    is.na(planting_date) | is.na(harvest_date) ~
      mean(yday(harvest_date) - plant_day,na.rm = TRUE),
    TRUE ~ yday(harvest_date) - plant_day
  ))%>%
  mutate(plant_day = case_when( # estimate planting day  from mean season length
    is.na(plant_day) ~ yday(harvest_date) - season_length,
    TRUE ~ plant_day
  ))%>%
  mutate(harvest_day = case_when( #estimate harvest day from mean season length
    is.na(harvest_date) ~ plant_day + season_length,
    TRUE ~ yday(harvest_date)
  ))%>%
  mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
                            levels = trial_ref[rev(order(ymd(first_sign_disease)))]))%>%
  ggplot() +
  geom_pointrange(aes(
    x = trial_ref,
    y = yday(first_sign_disease),
    ymin = plant_day,
    ymax = harvest_day,
    colour = cropping_season
   ))+
  scale_y_continuous(limits = c(
    -25,
    183),
    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1,7),sep = "-"),
    breaks = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-")))
    ) +
  geom_hline(yintercept = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-"))), 
             colour = "grey80",
             linetype = 2)+
  geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
  coord_flip() +
  scale_color_manual(values=c("black","grey70"))+
  ggtitle("Season length and first appearance of powdery mildew \nin each respective trial")+
  xlab("Trial reference code")+
  ylab(NULL)

```

>>>>

```{r Figure2, echo=FALSE, fig.cap="Season plot"}
PM_Mdat %>%
  distinct(trial_ref, planting_date, harvest_date, first_sign_disease) %>%
  mutate(planting_date = ymd(planting_date)) %>%
  mutate(harvest_date = ymd(harvest_date)) %>%
  mutate(first_sign_disease = ymd(first_sign_disease)) %>%
  mutate(cropping_season = case_when(
    # add categorical value for estimated season period
    is.na(planting_date) | is.na(harvest_date) ~ "Estimated",
    TRUE ~ "Actual"
  )) %>%
  mutate(plant_day = case_when(
    #for crops planted in late December minus 365 days from yday function
    yday(planting_date) < 200 ~ yday(planting_date),
    yday(planting_date) > 200 ~ yday(planting_date) - 365,
  )) %>%
  mutate(season_length = case_when(
    # when either planting date or harvest date are missing use the overall mean season length as an estimate
    is.na(planting_date) | is.na(harvest_date) ~
      mean(yday(harvest_date) - plant_day, na.rm = TRUE),
    TRUE ~ yday(harvest_date) - plant_day
  )) %>%
  mutate(plant_day = case_when(
    # estimate planting day  from mean season length
    is.na(plant_day) ~ yday(harvest_date) - season_length,
    TRUE ~ plant_day
  )) %>%
  mutate(harvest_day = case_when(
    #estimate harvest day from mean season length
    is.na(harvest_date) ~ plant_day + season_length,
    TRUE ~ yday(harvest_date)
  )) %>%
  mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
                            levels = trial_ref[rev(order(ymd(first_sign_disease)))])) %>%
  ggplot() +
  geom_pointrange(
    aes(
      x = trial_ref,
      y = yday(first_sign_disease),
      ymin = plant_day,
      ymax = harvest_day,
      colour = cropping_season
    )
  ) +
  scale_y_continuous(
    limits = c(-25,
               183),
    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1, 7), sep = "-"),
    breaks = yday(ymd(paste(
      rep(2018, 7), 1:7, rep(1, 7), sep = "-"
    )))
  ) +
  geom_hline(yintercept = yday(ymd(paste(
    rep(2018, 7), 1:7, rep(1, 7), sep = "-"
  ))),
  colour = "grey80",
  linetype = 2) +
  geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
  coord_flip() +
  scale_color_manual(values = c("black", "grey70")) +
  ggtitle("Season length and first appearance of powdery mildew\nin each respective trial") +
  xlab("Trial reference code") +
  ylab(NULL)
```
